Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-18 paper/icml_drau/framework.tex

We are thus interested in the behavior of reinforcement learning
algorithms in discretized environments, when the discretization timestep
is small. We will refer to such environments as \emph{near-continuous
environments}.

A formalized view of near continuous environments is
given below, along with $\deltat$-dependent definitions of return, discount
factor and value functions, that converge to well defined
continous-time limits. The state-action value
function is shown to collapse to the value function as $\deltat$ goes to $0$.
Consequently there is no Q-learning in continuous time, foreshadowing
problematic behaviors of near continuous time Q-learning.
%      \TODO{We should explain somwhere here that, if not invariant,
%      harder to find good hyperparameters} DONE

@@

%       }

% TODO: For now, differential equation is the default, SDE is a footnote.
        Let ${\cal S} = \mathbb{R}^d$ be a set of states, and ${\cal A}$ be a set of
	actions. Consider the continuous \emph{Markov Decision Process} (MDP) defined by the \emph{Differential Equation}: %\TODO{Explain the intuition of Brownian in SDE}:
        \begin{equation}
		\label{eq:diffusion}
		ds = F(s, a)dt. % + \Sigma(s, a)\dbt.
              \end{equation}
        For any $\deltat$, the discrete MDP ${\cal
	M}_\deltat = \langle {\cal S}, {\cal A}, T_{\deltat}, r_\deltat,
      \gamma_\deltat\rangle$ is a discretization of the continuous MDP with
      \emph{time discretization} $\deltat$. The transition probability
      $T_\deltat(s, a, s')$ is a dirac on $s_\deltat$, where $s_\deltat$ is the
      state obtained
      when starting at $s_0 = s$ and maintaining $a_t=a$ constant for a time
      $\deltat$.
      This corresponds to an agent evolving in the continuous
      environment described by Eq. \eqref{eq:diffusion}, but who is
      only making observations and choosing actions every $\deltat$. We
      say the the MDP ${\cal M}_\deltat$ is near-continuous.\footnote{
	      We believe the results presented here to be true in a more general framework, where states
	      follow a \emph{Stochastic Differential Equation} $ds = F(s, a)dt.  + \Sigma(s, a)\dbt$, with
	      $B_t$ a multidimensional brownian motion and $\Sigma$ its associated covariance matrix. However,
      formal treatment of SDEs is generally tedious and out of the scope of this paper.}
      Informally $F: {\cal S}\times{\cal A}\rightarrow {\cal S}$ describes
	the dynamic of the environment. The agent interacts with the environment through a deterministic policy function
	$\pi \colon {\cal S} \rightarrow {\cal A}$. Determinism of the policy is assumed to prevent problematic definitions
	of the value function in continuous time. This is only a mild requirement, as we introduce an off-policy algorithm,
	and only impose determinism of the exploitation policy.
	% This framework covers classical control theory, as well as many usual simulated environments. TODO: not convinced that this is relevant here.

%      \footnote{Informally, $T_\deltat(s, a, s')$ is approximately
%	      the probability distribution of $s + F(s, a)\deltat +
%	      \sqrt{\deltat}\Sigma(s, a){\cal N}(0, I)$, which is the
%	      discretization of Eq. \eqref{eq:diffusion} \TODO{CITE}}.
        In this paper, we try to design RL methods for near continuous MDP
	robust to the choice of $\deltat$. For robustness, a necessary condition is to remain viable when $\deltat \rightarrow 0$. Our method is thus to analyse the different
	quantities involved when $\deltat \rightarrow 0$, and make sure that they converge to meaningful limits.

        The first step in that direction is to check that the discretized
          trajectories converge to the continuous ones. 
	\begin{theorem}
		Assume that $\pi: {\cal S} \rightarrow {\cal A}$ is a continuous and
		deterministic policy. Let $(s_t)_{t\in\mathbb{R}_+}$ be the
		continuous process obtained by following \eqref{eq:diffusion} and
		$(s_\deltat^k)$ be the discrete process obtained if the agent only
		get observations and interacts with the environment every $\deltat$ \TODO{explain better}.

		We define the time process $\tilde s_\deltat^t = s^{\lfloor
		\frac{t}{\deltat}\rfloor}_\deltat$ for
		$t\in\mathbb{R_+}$.\TODO{Explain}. Then:
		\begin{equation}
			\label{eq:conv-traj}
			(\tilde s_\deltat^t)_{t\in\mathbb{R}_+} 
			\xrightarrow[\deltat \rightarrow 0]{} (s_t)_{t\in\mathbb{R}_+}.
		\end{equation}
	\end{theorem}

@@

	In what follows, $\deltat$-dependant scalings of the discount factor $\gamma_\deltat$
	and the reward $r_\deltat$ are given. These definitions fit the discrete case
	scenario when $\deltat=1$, and yields well defined, non trivial returns
	and value functions when $\deltat$ goes to $0$.

\paragraph{Return and Discount Factor}
For a continuous MDP and a continuous trajectory $\tau = (s_t, a_t)_t$,
the return is defined as~\cite{cont_rl}
\begin{equation}
	\label{eq:continuous-return}
	R(\tau) = \int_{t=0}^\infty\gamma^tr(s_t, a_t)dt.
\end{equation}

The natural discretization of this equation, if we want to define a discretized
return $R_\delta$ for each $\deltat$ is:
\begin{equation}
	\label{eq:discretized-return}
	R_\deltat(\tau) = \sum_{k=0}^\infty\gamma^{k\deltat}
	r(s_\deltat^k, a_\deltat^k)\deltat
\end{equation}

Natural definitions of $\gamma_\deltat$ and $r_\deltat$ such
that the return defined in equation (\ref{eq:discretized-return}) corresponds
to the discrete return for the MDP ${\cal M}_\deltat$ follow:
\begin{align}
	\label{eq:def-gamma}
	\gamma_\deltat =& \gamma^\deltat\\
	\label{eq:def-reward}
	r_\deltat =& \deltat . r.
\end{align}
% Thus, we see that the natural discretization of a continuous MDP ${\cal M} = \langle {\cal S}, {\cal A}, T, r, \gamma\rangle$ is ${\cal M}_\deltat = \langle {\cal S}, {\cal A}, T_\deltat, r\deltat, \gamma^\deltat\rangle$.

@@

      \paragraph{Number of steps / Physical time, Time horizon}
        % [[I prefer to talk about ``number of steps'' VS ``Physical time'' than microscopic/Macroscopic]]
        In near continuous environments, there are two notions of time,
	the number of steps, or the number of actions taken, and the actual amount of time spent
	in the underlying continuous time environment, which we call the physical
	time. If $t$ is the real time and $k$ the number of steps, the two are related through $t = k \deltat$.

	The notion of time horizon, which is, informally, the amount of time on
	which the agent optimizes its return, is only meaningful in physical
	time.
        %Having a time horizon of $10$ steps means something very different
	%if $\deltat = 0.1$ and if $\deltat = 0.0001$.
        A rule of thumb
	is that the time horizon of an agent with discount factor $\gamma$ is
	of order $\frac{1}{1 - \gamma}$ steps. If $\gamma_\deltat$ was left constant
	as $\deltat$ goes to $0$, the corresponding time horizon in physical time
	would write as $\frac{\deltat}{1 - \gamma}$ which goes to $0$ when
	$\deltat$ goes to $0$.
        On the contrary, the definition of $\gamma_\deltat$ in
	Eq.~\eqref{eq:def-gamma} yields an approximately constant
	time horizon in physical time when $\deltat$ goes to $0$. Indeed,
	\begin{equation}
          \label{eq:time-horizon}
          \frac{\deltat}{1-\gamma^\deltat}
          = - \frac{1}{\log \gamma} + \bigO(\deltat)
          \approx \frac{1}{1-\gamma},
        \end{equation}
        approximately invariant to $\deltat$ when $\deltat$ goes to 0.

@@

The definition of the return Eq.~\eqref{eq:continuous-return}, yields the
following definition of the continuous value function
\begin{align}
  V^\pi(s) =& \E_{\tau\sim\pi}\left[R(\tau) \mid s_0 = s\right]\\
  =& \E_{\tau\sim\pi}\left[\int\limits_{0}^\infty \gamma^{t} r(s_t, a_t) dt \mid s_0 = s\right].
\end{align}
The corresponding discretization for time discretization $\deltat$ is
\begin{align}
  V^\pi_\deltat(s) =& \E_{\tau\sim\pi}\left[R_\deltat(\tau) \mid s_0 = s\right]\\
  =& \E_{\tau\sim\pi}\left[\sum\limits_{k=0}^\infty \gamma^{k\deltat}r(s^k_{\deltat}, a^k_{\deltat})\deltat \mid s_0 = s\right]
\end{align}
which fits the usual definition of the discrete V-function for $\gamma_\deltat$ and
$r_\deltat$ defined in~(\ref{eq:def-gamma}, \ref{eq:def-reward}).
The discretized value function follows the Bellman equation\footnote{
	If the continuous MDP dynamic follows~\eqref{eq:diffusion}, the limit of the Bellman equation for $V^\pi_\deltat$ when $\deltat \rightarrow 0$ is the Hamilton-Jacobi-Bellman equation on $V^\pi$ \cite{cont_rl}
\begin{equation}
  \label{eq:hamilton-jacobi-bellman}
  r + \partial_s V^\pi \cdot F = - \log(\gamma) V^\pi
\end{equation}}

@@

\subsection{There is no Q-function in continuous time}

Contrary to the Value function, the Action-Value function $Q$ is ill-defined
for a continuous MDP. More precisely, the Q-function  collapses to the
V-function when $\deltat \rightarrow 0$. In near continuous time, the effect of
individual actions on the Q-function is of order $\bigO(\deltat)$. This makes
deriving a ranking of action from an approximate Q-function difficult.
Formally:
\begin{theorem}
	Let $\pi$ be a deterministic policy such that for all $\deltat$, $V^\pi_\deltat$ is continuously
	differentiable, then, for all $s, a$,
	\begin{equation}
		\label{eq:q-discr}
		Q^\pi_\deltat(s, a) = V^\pi(s) + \bigO\left(\deltat\right)
	\end{equation}

@@

A consequence of Theorem \ref{th:q-cont} is that in exact continuous time,
$Q^\pi$ does not bear any information on the ranking of actions, and
thus cannot be used to select actions that yields higher future returns. There is no time continuous Q-learning.

\begin{proof}
	Bellman equation for the discretized Q-function yields
  \begin{align}
    Q^\pi_\deltat(s, a) &= r(s, a)\deltat + \gamma^\deltat \E_{s'|s, a}\left[V^\pi_\deltat(s')\right] 
  \end{align}
  From the environment dynamic equation, 
  \begin{equation}
	  s' = s + f(s, a) \deltat + \smallo(\deltat).
  \end{equation}As $V^\pi$ is assumed to be continuously differentiable,
  \begin{align}
	  V^\pi_\deltat(s') &= V^\pi_\deltat(s) + \partial_s V^\pi_\deltat(s) F(s, a)\deltat + \smallo(\deltat)\\
			    &= V^\pi_\deltat(s) + \bigO(\deltat)
  \end{align}
  Rewriting $Q^\pi_\deltat$ yields
  \begin{align}
	  Q^\pi_\deltat(s, a) &= r(s, a)\deltat + \gamma^\deltat (V^\pi_\deltat(s) + \bigO(\deltat))\\
			      &= (1 + \bigO(\deltat)) (V^\pi_\deltat(s) + \bigO(\deltat)) + \bigO(\deltat)\\
			      &= V^\pi_\deltat(s) + \bigO(\deltat).
  \end{align}
  Now, using Thm.~\ref{th:conv-value},
  \begin{align}
	  Q^\pi_\deltat(s, a) = V^\pi(s) + \bigO(\deltat)
  \end{align}
  which ends the proof.
%  But we know that $s'$ is close to $s$. If we define $\delta s = s' - s$, then:
%  \begin{equation}
%    \E_{s'|s, a}\left[\delta s\right] = \bigO(\deltat) \quad \text{Var}(\delta s) = \bigO(\deltat)
%  \end{equation}
%  \TODO{Explain. And this is not exactly the Variance.} Therefore:
%  \begin{align}
%    |\E_{s'|s, a}\left[V^\pi_\deltat(s')\right] - V^\pi_\deltat(s)| &= \E_{\delta s|s, a}\left[\partial_s V^\pi_\deltat\cdot \delta s +\bigO(\|\delta s\|^2)\right]\nonumber\\
%                                            &\leq \|\partial_s V_\deltat^\pi\|\cdot \|\E_{\delta s|s, a}\left[\delta s\right]\| +\bigO(\delta t)\nonumber\\
%    &= \bigO(\deltat)\nonumber
%  \end{align}
%  Finally:
%  \begin{align}
%    Q^\pi_\deltat(s, a) &= r(s, a)\deltat + \gamma^\deltat \E_{s'|s, a}\left[V_\deltat^\pi(s')\right] \nonumber\\
%                &= r(s, a)\deltat + \left(1 + \bigO(\deltat)\right)(V^\pi(s) + \bigO(\deltat))\nonumber\\
%    &= V^\pi(s) + \bigO(\deltat)\nonumber
%  \end{align}
  \end{proof}

>>>>

We are thus interested in the behavior of reinforcement learning
algorithms in discretized environments, when the discretization timestep
is small. We will refer to such environments as \emph{near-continuous
environments}.
A formalized view of near-continuous environments is
given below, along with $\deltat$-dependent definitions of return, discount
factor and value functions, that converge to well defined
continous-time limits. The state-action value
function is shown to collapse to the value function as $\deltat$ goes to $0$.
Consequently there is no $Q$-learning in continuous time, foreshadowing
problematic behaviors of near continuous time $Q$-learning.
%      \TODO{We should explain somwhere here that, if not invariant,
%      harder to find good hyperparameters} DONE

@@

g
%       }

% TODO: For now, differential equation is the default, SDE is a footnote.
Let ${\cal S} = \mathbb{R}^d$ be a set of states, and ${\cal A}$ be a set of
actions. Consider the continuous \emph{Markov Decision Process} (MDP) defined by the differential equation %\TODO{Explain the intuition of Brownian in SDE}:
        \begin{equation}
g	\label{eq:diffusion}
g	ds = F(s, a)dt. % + \Sigma(s, a)\dbt.
              \end{equation}
        For any $\deltat$, the discrete MDP ${\cal
gM}_\deltat = \langle {\cal S}, {\cal A}, T_{\deltat}, r_\deltat,
      \gamma_\deltat\rangle$ is a discretization of the continuous MDP with
      \emph{time discretization} $\deltat$. Here the deterministic
      transition function
      $T_\deltat(s, a, s')$ is %a dirac on $s_\deltat$, where $s_\deltat$ is 
      the
      state obtained
      when starting at $s_0 = s$ and maintaining $a_t=a$ constant for a time
      $\deltat$.
      This corresponds to an agent evolving in the continuous
      environment described by Eq. \eqref{eq:diffusion}, but 
      only making observations and choosing actions every $\deltat$. We
      call such an  MDP ${\cal M}_\deltat$
      near-continuous.\footnote{
g      We believe the results presented here hold more
g      generallly, assuming states
g      follow a \emph{Stochastic Differential Equation} \begin{equation}
g	      ds = F(s, a)dt  + \Sigma(s, a)\dbt
g	      \label{eq:sde}
      \end{equation} with
g      $B_t$ a multidimensional Brownian motion and $\Sigma$ a covariance matrix. A
      formal treatment of SDEs is beyond the scope of this paper.}
      Informally $F: {\cal S}\times{\cal A}\rightarrow {\cal S}$ describes
gthe dynamic of the environment. The agent interacts with the environment through a deterministic policy function
g$\pi \colon {\cal S} \rightarrow {\cal A}$. Determinism of the policy is assumed to prevent problematic definitions
gof the value function in continuous time. This is only a mild requirement, as we introduce an off-policy algorithm,
gand only impose determinism of the exploitation policy.
g% This framework covers classical control theory, as well as many usual simulated environments. TODO: not convinced that this is relevant here.

%      \footnote{Informally, $T_\deltat(s, a, s')$ is approximately
%	      the probability distribution of $s + F(s, a)\deltat +
%	      \sqrt{\deltat}\Sigma(s, a){\cal N}(0, I)$, which is the
%	      discretization of Eq. \eqref{eq:diffusion} \TODO{CITE}}.
        %In this paper, we try to design RL methods for near continuous MDP
g%robust to the choice of $\deltat$. 
g
gA necessary condition for robustness of an algorithm for
gnear-continuous time MDPs is 
gto remain viable when $\deltat \rightarrow 0$. Thus we will try to
gmake sure the various quantities involved converge to meaningful
glimits when $\deltat\to 0$.

        The first step in that direction is to check that the discretized
          trajectories converge to the continuous ones. 
g\begin{theorem}
g	Assume that $\pi: {\cal S} \rightarrow {\cal A}$ is a continuous and
g	deterministic policy. Let $(s_t)_{t\in\mathbb{R}_+}$ be the
g	continuous process obtained by following \eqref{eq:diffusion} and
g	$(s_\deltat^k)$ be the discrete process obtained if the agent only
g	get observations and interacts with the environment every $\deltat$ \TODO{explain better}.

g	We define the time process $\tilde s_\deltat^t = s^{\lfloor
g	\frac{t}{\deltat}\rfloor}_\deltat$ for
g	$t\in\mathbb{R_+}$.\TODO{Explain}. Then:
g	\begin{equation}
g		\label{eq:conv-traj}
g		(\tilde s_\deltat^t)_{t\in\mathbb{R}_+} 
g		\xrightarrow[\deltat \rightarrow 0]{} (s_t)_{t\in\mathbb{R}_+}.
g	\end{equation}
g\end{theorem}

@@

gIn what follows, $\deltat$-dependant scalings of the discount factor $\gamma_\deltat$
gand the reward $r_\deltat$ are given. These definitions fit the discrete case
gscenario when $\deltat=1$, and yields well defined, non trivial returns
gand value functions when $\deltat$ goes to $0$.

\paragraph{Return and Discount Factor}
For a continuous MDP and a continuous trajectory $\tau = (s_t, a_t)_t$,
the return is defined as~\cite{cont_rl}
\begin{equation}
g\label{eq:continuous-return}
gR(\tau) = \int_{t=0}^\infty\gamma^tr(s_t, a_t)dt.
\end{equation}

The natural discretization of this equation, if we want to define a discretized
return $R_\delta$ for each $\deltat$ is:
\begin{equation}
g\label{eq:discretized-return}
gR_\deltat(\tau) = \sum_{k=0}^\infty\gamma^{k\deltat}
gr(s_\deltat^k, a_\deltat^k)\deltat
\end{equation}

Natural definitions of $\gamma_\deltat$ and $r_\deltat$ such
that the return defined in equation (\ref{eq:discretized-return}) corresponds
to the discrete return for the MDP ${\cal M}_\deltat$ follow:
\begin{align}
g\label{eq:def-gamma}
g\gamma_\deltat =& \gamma^\deltat\\
g\label{eq:def-reward}
gr_\deltat =& \deltat . r.
\end{align}
% Thus, we see that the natural discretization of a continuous MDP ${\cal M} = \langle {\cal S}, {\cal A}, T, r, \gamma\rangle$ is ${\cal M}_\deltat = \langle {\cal S}, {\cal A}, T_\deltat, r\deltat, \gamma^\deltat\rangle$.

@@

      \paragraph{Number of steps / Physical time, Time horizon}
        % [[I prefer to talk about ``number of steps'' VS ``Physical time'' than microscopic/Macroscopic]]
        In near continuous environments, there are two notions of time,
gthe number of steps, or the number of actions taken, and the actual amount of time spent
gin the underlying continuous time environment, which we call the physical
gtime. If $t$ is the real time and $k$ the number of steps, the two are related through $t = k \deltat$.

gThe notion of time horizon, which is, informally, the amount of time on
gwhich the agent optimizes its return, is only meaningful in physical
gtime.
        %Having a time horizon of $10$ steps means something very different
g%if $\deltat = 0.1$ and if $\deltat = 0.0001$.
        A rule of thumb
gis that the time horizon of an agent with discount factor $\gamma$ is
gof order $\frac{1}{1 - \gamma}$ steps. If $\gamma_\deltat$ was left constant
gas $\deltat$ goes to $0$, the corresponding time horizon in physical time
gwould write as $\frac{\deltat}{1 - \gamma}$ which goes to $0$ when
g$\deltat$ goes to $0$.
        On the contrary, the definition of $\gamma_\deltat$ in
gEq.~\eqref{eq:def-gamma} yields an approximately constant
gtime horizon in physical time when $\deltat$ goes to $0$. Indeed,
g\begin{equation}
          \label{eq:time-horizon}
          \frac{\deltat}{1-\gamma^\deltat}
          = - \frac{1}{\log \gamma} + \bigO(\deltat)
          \approx \frac{1}{1-\gamma},
        \end{equation}
        approximately invariant to $\deltat$ when $\deltat$ goes to 0.

@@

The definition of the return Eq.~\eqref{eq:continuous-return}, yields the
following definition of the continuous value function
\begin{align}
  V^\pi(s) =& \E_{\tau\sim\pi}\left[R(\tau) \mid s_0 = s\right]\\
  =& \E_{\tau\sim\pi}\left[\int\limits_{0}^\infty \gamma^{t} r(s_t, a_t) dt \mid s_0 = s\right].
\end{align}
The corresponding discretization for time discretization $\deltat$ is
\begin{align}
  V^\pi_\deltat(s) =& \E_{\tau\sim\pi}\left[R_\deltat(\tau) \mid s_0 = s\right]\\
  =& \E_{\tau\sim\pi}\left[\sum\limits_{k=0}^\infty \gamma^{k\deltat}r(s^k_{\deltat}, a^k_{\deltat})\deltat \mid s_0 = s\right]
\end{align}
which fits the usual definition of the discrete V-function for $\gamma_\deltat$ and
$r_\deltat$ defined in~(\ref{eq:def-gamma}, \ref{eq:def-reward}).
The discretized value function follows the Bellman equation\footnote{
gIf the continuous MDP dynamic follows~\eqref{eq:diffusion}, the limit of the Bellman equation for $V^\pi_\deltat$ when $\deltat \rightarrow 0$ is the Hamilton-Jacobi-Bellman equation on $V^\pi$ \cite{cont_rl}
\begin{equation}
  \label{eq:hamilton-jacobi-bellman}
  r + \partial_s V^\pi \cdot F = - \log(\gamma) V^\pi
\end{equation}}

@@

\subsection{There is no $Q$-function in continuous time}

Contrary to the Value function, the Action-Value function $Q$ is ill-defined
for a continuous MDP. More precisely, the $Q$-function  collapses to the
V-function when $\deltat \rightarrow 0$. In near continuous time, the effect of
individual actions on the $Q$-function is of order $\bigO(\deltat)$. This makes
deriving a ranking of action from an approximate $Q$-function difficult.
Formally:
\begin{theorem}
gLet $\pi$ be a deterministic policy such that for all $\deltat$, $V^\pi_\deltat$ is continuously
gdifferentiable, then, for all $s, a$,
g\begin{equation}
g	\label{eq:q-discr}
g	Q^\pi_\deltat(s, a) = V^\pi(s) + \bigO\left(\deltat\right)
g\end{equation}

@@

A consequence of Theorem \ref{th:q-cont} is that in exact continuous time,
$Q^\pi$ does not bear any information on the ranking of actions, and
thus cannot be used to select actions that yields higher future returns. There is no time continuous $Q$-learning.

\begin{proof}
gBellman equation for the discretized $Q$-function yields
  \begin{align}
    Q^\pi_\deltat(s, a) &= r(s, a)\deltat + \gamma^\deltat \E_{s'|s, a}\left[V^\pi_\deltat(s')\right] 
  \end{align}
  From the environment dynamic equation, 
  \begin{equation}
g  s' = s + f(s, a) \deltat + \smallo(\deltat).
  \end{equation}As $V^\pi$ is assumed to be continuously differentiable,
  \begin{align}
g  V^\pi_\deltat(s') &= V^\pi_\deltat(s) + \partial_s V^\pi_\deltat(s) F(s, a)\deltat + \smallo(\deltat)\\
g		    &= V^\pi_\deltat(s) + \bigO(\deltat)
  \end{align}
  Rewriting $Q^\pi_\deltat$ yields
  \begin{align}
g  Q^\pi_\deltat(s, a) &= r(s, a)\deltat + \gamma^\deltat (V^\pi_\deltat(s) + \bigO(\deltat))\\
g		      &= (1 + \bigO(\deltat)) (V^\pi_\deltat(s) + \bigO(\deltat)) + \bigO(\deltat)\\
g		      &= V^\pi_\deltat(s) + \bigO(\deltat).
  \end{align}
  Now, using Thm.~\ref{th:conv-value},
  \begin{align}
g  Q^\pi_\deltat(s, a) = V^\pi(s) + \bigO(\deltat)
  \end{align}
  which ends the proof.
%  But we know that $s'$ is close to $s$. If we define $\delta s = s' - s$, then:
%  \begin{equation}
%    \E_{s'|s, a}\left[\delta s\right] = \bigO(\deltat) \quad \text{Var}(\delta s) = \bigO(\deltat)
%  \end{equation}
%  \TODO{Explain. And this is not exactly the Variance.} Therefore:
%  \begin{align}
%    |\E_{s'|s, a}\left[V^\pi_\deltat(s')\right] - V^\pi_\deltat(s)| &= \E_{\delta s|s, a}\left[\partial_s V^\pi_\deltat\cdot \delta s +\bigO(\|\delta s\|^2)\right]\nonumber\\
%                                            &\leq \|\partial_s V_\deltat^\pi\|\cdot \|\E_{\delta s|s, a}\left[\delta s\right]\| +\bigO(\delta t)\nonumber\\
%    &= \bigO(\deltat)\nonumber
%  \end{align}
%  Finally:
%  \begin{align}
%    Q^\pi_\deltat(s, a) &= r(s, a)\deltat + \gamma^\deltat \E_{s'|s, a}\left[V_\deltat^\pi(s')\right] \nonumber\\
%                &= r(s, a)\deltat + \left(1 + \bigO(\deltat)\right)(V^\pi(s) + \bigO(\deltat))\nonumber\\
%    &= V^\pi(s) + \bigO(\deltat)\nonumber
%  \end{align}
  \end{proof}
